\LARGE \bf Exploiting Non-Slip Wall Contacts \\ to Position Two Particles Using The Same Control Input

### 2018-12-06 journalWallFriction/theory2robAlgs.tex
Added new Fig 4, the caption needs to be changed, but just for Dr. Becker to see if it is what he wants.

\subsection{Convex Polygonal Workspaces: 2-Move Reachable Set}
   \begin{figure}
\centering
\renewcommand{\figwid}{0.8\columnwidth}
{\begin{overpic}[width =\figwid]{differentNumSides.pdf}\put(5,100){Workspace}\put(20,100){$\Delta$ configuration space}
\end{overpic}
}
\caption{\label{fig:polygon}{The $\Delta$ configuration space is all possible configurations of $p_2-p_1$. The sets reachable in two moves, called \emph{2-move reachable sets}, are drawn with transparent blue polygons. A polygon with $n$ sides has $n$ 2-move reachable sets, but if $n$ is even and the polygon is regular, half the reachable sets overlap. If $\Delta g$ is in the 2-move reachable sets, we can achieve the required relative position in two moves. If $\Delta g$ is not in the 2-move reachable set, we define a temporary goal $\Delta g_c$ (the closest point on the 2-move reachable set to $\Delta g$) and apply two moves to achieve $\Delta g_c$. We repeat this process until the relative goal position is achieved.
%Workspace and $\Delta$ configuration spaces for different polygonal workspaces and their representative $\Delta$ configuration spaces and reachable sets. As the number of sides in the polygon increases, the total area of the $\Delta$ configuration space is four times of the workspace.
}
\vspace{-1em}
}
\end{figure}

>>>>

\subsection{Convex Polygonal Workspaces: 2-Move Reachable Set}
   \begin{figure}
\centering
\renewcommand{\figwid}{0.8\columnwidth}
{\begin{overpic}[width =\figwid]{differentNumSides.pdf}\put(5,102){Workspace}\put(20,102){$\Delta$ configuration space}
\end{overpic}
}
\caption{\label{fig:polygon}{The $\Delta$ configuration space is all possible configurations of $p_2-p_1$. The sets reachable in two moves, called \emph{2-move reachable sets}, are drawn with transparent blue polygons. A polygon with $n$ sides has $n$ 2-move reachable sets, but if $n$ is even and the polygon is regular, half the reachable sets overlap. If $\Delta g$ is in the 2-move reachable sets, we can achieve the required relative position in two moves. %If $\Delta g$ is not in the 2-move reachable set, we define a temporary goal $\Delta g_c$ (the closest point on the 2-move reachable set to $\Delta g$) and apply two moves to achieve $\Delta g_c$. We repeat this process until the relative goal position is achieved.
%Workspace and $\Delta$ configuration spaces for different polygonal workspaces and their representative $\Delta$ configuration spaces and reachable sets. As the number of sides in the polygon increases, the total area of the $\Delta$ configuration space is four times of the workspace.
}
\vspace{-1em}
}
\end{figure}
